---
title: "Effect of labels on categoricality and aligment"
author: "Gary Lupyan, Ellise Suffill"
date: "2023-06-21"
output:
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: true
    toc: true
    code_folding: hide
---

```{r, setup, include=F, cache=FALSE,message = FALSE}
library(Rmisc)
library(tidyverse)
library(lme4)
library(ggplot2)
library(directlabels)
colors <- c("#000000", "#E69F00", "#56B4E9")
```


# Study 1

```{r, warning=FALSE, cache=FALSE,message = FALSE}
indiv_df_1 <- read.csv(file="data/CEL_1_indiv_data.tsv", header=T, sep="\t") %>% 
	mutate(Condition = case_when(
		cond_numeric<0 ~ "Baseline",
		cond_numeric==0 ~ "No Labels",
		cond_numeric>0 ~ "With Labels"),
		exp = "exp1")
		
pairwise_df_1 <- read.csv(file="data/CEL_1_pairwise_data.tsv", header=T, sep="\t")
```

## Effect of condition on categoricality as log(between/within)


```{r}
indiv_df_1 %>% group_by(Condition) %>% 
	summarize(categoricality = mean(log_cat_ratio), sd=sd(log_cat_ratio))
```


Categoricality significantly higher in sorts from with labels condition, compared with no labels and baseline conditions.

```{r, warning=FALSE,message = FALSE}
no_labels_vs_all <- lm(formula=log_cat_ratio ~ relevel(as.factor(cond_numeric), ref='1'), data=indiv_df_1)
baseline_vs_all <- lm(formula=log_cat_ratio ~ relevel(as.factor(cond_numeric), ref='-1'), data=indiv_df_1)
summary(no_labels_vs_all)
summary(baseline_vs_all)
```


### Categoricality figure - line
```{r, warning=FALSE, echo=TRUE,message = FALSE}
categoricality_agg <- indiv_df_1 %>%
	mutate(
		between_category = ab_dist,
		within_category = (a_dist+b_dist)/2) %>% 
	pivot_longer(cols=c(between_category,within_category),names_to="Category_comp",values_to = "dist") %>% 
	summarySEwithin(measurevar = "dist", withinvars = "Category_comp", betweenvars="Condition")



ggplot(data=filter(categoricality_agg), aes(x=Category_comp, y=dist, group=Condition, color=Condition)) +
  ylim(300, 600)+
	theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  theme(panel.border = element_blank(), axis.line = element_line())+
  theme(text=element_text(size=20))+
	scale_x_discrete(labels=c("Between Category","Within Category"))+
  xlab("\nCategory comparison") + ylab("Average Euclidean distance\n")+
  theme(legend.position = "none")

ggsave("plots/CEL_1_categoricality_line_placeholder.pdf",width=1000,height=700,units='px',dpi=144)


ggplot(data=filter(categoricality_agg,Condition=="Baseline"), aes(x=Category_comp, y=dist, group=Condition, color=Condition)) +
  geom_line(aes(linetype=Condition,group=Condition), size=1,position=position_dodge(width=.05)) +
  geom_point(size=2,position=position_dodge(width=.05)) +
  geom_errorbar(mapping=aes(x=Category_comp, ymin=dist-se, ymax=dist+se), size=1, width=.05,position=position_dodge(width=.05)) +
  geom_dl(aes(label=Condition), method=list("last.qp", cex=1.2),
          position=position_nudge(x=.1)) +
  ylim(300, 600)+
	theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  theme(panel.border = element_blank(), axis.line = element_line())+
  theme(text=element_text(size=20))+
	scale_x_discrete(labels=c("Between Category","Within Category"))+
  xlab("\nCategory comparison") + ylab("Average Euclidean distance\n")+
  theme(legend.position = "none")

ggsave("plots/CEL_1_categoricality_line_baseline_only.pdf",width=1000,height=700,units='px',dpi=144)	



ggplot(data=filter(categoricality_agg,Condition!="With Labels"), aes(x=Category_comp, y=dist, group=Condition, color=Condition)) +
  geom_line(aes(linetype=Condition,group=Condition), size=1,position=position_dodge(width=.05)) +
  geom_point(size=2,position=position_dodge(width=.05)) +
  geom_errorbar(mapping=aes(x=Category_comp, ymin=dist-se, ymax=dist+se), size=1, width=.05,position=position_dodge(width=.05)) +
  geom_dl(aes(label=Condition), method=list("last.qp", cex=1.2),
          position=position_nudge(x=.1)) +
  ylim(300, 600)+
	theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  theme(panel.border = element_blank(), axis.line = element_line())+
  theme(text=element_text(size=20))+
	scale_x_discrete(labels=c("Between Category","Within Category"))+
  xlab("\nCategory comparison") + ylab("Average Euclidean distance\n")+
  theme(legend.position = "none")

ggsave("plots/CEL_1_categoricality_line_no_labels.pdf",width=1000,height=700,units='px',dpi=144)	


ggplot(data=categoricality_agg, aes(x=Category_comp, y=dist, group=Condition, color=Condition)) +
  geom_line(aes(linetype=Condition,group=Condition), size=1,position=position_dodge(width=.05)) +
  geom_point(size=2,position=position_dodge(width=.05)) +
  geom_errorbar(mapping=aes(x=Category_comp, ymin=dist-se, ymax=dist+se), size=1, width=.05,position=position_dodge(width=.05)) +
  geom_dl(aes(label=Condition), method=list("last.qp", cex=1.2),
          position=position_nudge(x=.1)) +
  ylim(300, 600)+
	theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  theme(panel.border = element_blank(), axis.line = element_line())+
  theme(text=element_text(size=20))+
	scale_x_discrete(labels=c("Between Category","Within Category"))+
  xlab("\nCategory comparison") + ylab("Average Euclidean distance\n")+
  theme(legend.position = "none")

ggsave("plots/CEL_1_categoricality_line_all.pdf",width=1000,height=700,units='px',dpi=144)	
	

```


### Categoricality figure - violin
```{r}
means <- indiv_df_1 %>%
  group_by(Condition) %>%
  summarise(Categoricality = mean(log_cat_ratio))

ggplot(indiv_df_1, aes(y=log_cat_ratio, x=Condition, color=Condition, fill=Condition)) +
  geom_violin(alpha=.5) +
	scale_color_manual(values= colors) +
  scale_fill_manual(values= colors) +
  geom_hline(data=means, aes(yintercept=Categoricality, color=Condition), alpha=.5, size=1) +
  geom_boxplot(width=0.1, alpha=.5) +
  theme_bw() +
  ylab("Categoricality") +
  theme(text=element_text(size=20)) +
	coord_cartesian(ylim=c(-.05,3.3))+
  theme(legend.position="blank") +
  theme(panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())
  
ggsave("plots/CEL_1_categoricality_violin.pdf")
```


## Effect of condition on the number of clusters formed during free sort


Label participants produce sorts with significantly fewer clusters

```{r}
indiv_df_1 %>% group_by(Condition) %>% summarize(num_clusters =round(mean(n_clusters),1))
```



Poisson model (shown by likelihood ratio test to be nearly identical to the negative binomial model)

```{r}
nb_counts <- indiv_df_1 %>% MASS::glm.nb(formula=n_clusters ~ relevel(as.factor(cond_numeric), ref='1'), data=.) 
poisson_counts <- indiv_df_1 %>% glm(formula=n_clusters ~ relevel(as.factor(cond_numeric), ref='1'), data=.,family=poisson)
pchisq(2 * (logLik(nb_counts) - logLik(poisson_counts)), df = 1, lower.tail = FALSE)
summary(poisson_counts)
```


Label participants are marginally more likely to produce 2-cluster sorts 

```{r, warning=FALSE,message = FALSE}

prop_2_cluster_sort <- indiv_df_1 %>%
  group_by(cond_numeric) %>%
  summarise(n_clusters = mean(n_clusters==2))
prop_2_cluster_sort

m1 <- glm(I(n_clusters==2) ~ relevel(as.factor(cond_numeric), ref='1'), data=indiv_df_1,family=binomial)
summary(m1)

```

### Cluster figure
```{r, warning=FALSE,message = FALSE, echo=TRUE}
means <- indiv_df_1 %>%
  dplyr::group_by(Condition) %>%
  dplyr::summarise(Clusters = mean(n_clusters))

ggplot(indiv_df_1, aes(x=n_clusters, fill=Condition)) +
  geom_histogram(alpha=0.9,position="dodge", binwidth=0.5)+
	scale_y_continuous(breaks = seq(0, 30, 5))+
  scale_x_continuous(breaks = seq(1, 10, 1.00))+
  labs(caption = "", size=20) +  
  theme_minimal() +
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank()) +
  geom_hline(yintercept = c(0,5,10,15,20,25), alpha = 0.15) +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  ylab("Frequency") + 
  xlab("Number of clusters used") +
	coord_cartesian(ylim=c(0,30),xlim=c(2,9))+
  theme(axis.text.x = element_text(size=13),
       axis.title.y = element_text(size=15),
       axis.title.x = element_text(size=15))+
  theme(legend.position = c(.4, .7))

ggsave("plots/CEL_1_n_clusters_histogram.pdf")
```




## Effect of condition on alignment (aggregated by a and b participants in each pair)

Alignment significantly higher in with labels, compared with no labels and baseline

```{r, warning=FALSE,message = FALSE}

pairwise_df_1 <- pairwise_df_1 %>% 
	mutate(cat_min = pmin(cat_diff_log_ratio_a, cat_diff_log_ratio_b),
				 cluster_min = pmin(pp_a_n_clusters, pp_b_n_clusters),
				 cluster_max = pmax(pp_a_n_clusters, pp_b_n_clusters),
				 cluster_abs_diff = abs(pp_a_n_clusters-pp_b_n_clusters)
				 )

d_1a <- pairwise_df_1 %>%
  group_by(cond_numeric,Condition,participant_a) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>%
  rename(participant = participant_a)
d_1b <- pairwise_df_1 %>%
  group_by(cond_numeric,Condition,participant_b) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>%
  rename(participant = participant_b)
d_1_all <- rbind(d_1a,d_1b) %>%
  group_by(cond_numeric,Condition,participant) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>% 
	rename(mean_alignment = z_transformed_rank_r)

#residualize categoricality from alignment for later analysis
d_1_all$mean_alignment_adj <- resid(lm(mean_alignment ~ cat_min, data=d_1_all))
d_1_all$exp <- "exp1"

d_1_all %>% group_by(Condition) %>% summarize(alignment = mean(mean_alignment), sd=(sd(mean_alignment)),n=n())

labels_vs_all <- lm(formula=mean_alignment ~ relevel(as.factor(cond_numeric), ref='1'), data=d_1_all)
baseline_vs_all <- lm(formula=mean_alignment ~ relevel(as.factor(cond_numeric), ref='-1'), data=d_1_all)

summary(labels_vs_all)
summary(baseline_vs_all)
```
### Alignment plot

```{r, warning=FALSE, echo=TRUE,message = FALSE}
means <- d_1_all %>%
  group_by(Condition) %>%
  summarise(Alignment = mean(mean_alignment))

ggplot(d_1_all, aes(y=mean_alignment, x=Condition, color=Condition, fill=Condition)) +
  geom_violin(alpha=.5) +
  geom_hline(data=means, aes(yintercept=Alignment, col=Condition), alpha=.5, size=1) +
  geom_boxplot(width=0.1, alpha=.5) +
  theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  ylab("Alignment") +
  xlab("Condition") +
  theme(text=element_text(size=20)) +
	coord_cartesian(ylim=c(-.05,.7))+
	theme(legend.position="blank") +
  theme(panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())
  
ggsave("plots/CEL_1_alignment_violin.pdf")
```

## Alignment for participants who produced 2 clusters only

```{r}
participants_2_clusters_exp1 <- indiv_df_1 %>% filter(n_clusters==2) %>% select(participant)

d_1a_2cluster <- pairwise_df_1 %>% filter(participant_a %in% participants_2_clusters_exp1$participant & 
																 	participant_b %in% participants_2_clusters_exp1$participant) %>% 
  group_by(cond_numeric,Condition,participant_a) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>%
  rename(participant = participant_a)
d_1b_2cluster <- pairwise_df_1 %>% filter(participant_a %in% participants_2_clusters_exp1$participant & 
																 	participant_b %in% participants_2_clusters_exp1$participant) %>% 
  group_by(cond_numeric,Condition,participant_b) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>%
  rename(participant = participant_b)
d_1_all_2cluster <- rbind(d_1a_2cluster,d_1b_2cluster) %>%
  group_by(cond_numeric,Condition,participant) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>% 
	rename(mean_alignment = z_transformed_rank_r)

d_1_all_2cluster %>% group_by(Condition) %>% summarize(alignment = mean(mean_alignment), sd=(sd(mean_alignment)),n=n())

d_1_all_2cluster %>% lm(mean_alignment~relevel(as.factor(cond_numeric),ref="1"),data=.) %>% summary
```


## Effect of condition on alignment controlling for minimum categoricality by pair

After controlling for minimum categoricality by pair, no differences in alignment across conditions
```{r, warning=FALSE,message = FALSE}

d_1_all %>%  lm(mean_alignment~cat_min, data=.) %>% summary
d_1_all %>%  with(cor(mean_alignment,cat_min))

d_1_all %>%  lm(mean_alignment~cat_min+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary
```


## Effect of condition on alignment controlling for cluster nums

After controlling for minimum categoricality by pair, no differences in alignment across conditions
```{r, warning=FALSE,message = FALSE}

d_1_all %>%  with(cor.test(mean_alignment,cluster_min))
d_1_all %>%  with(cor.test(mean_alignment,cluster_max))
d_1_all %>%  with(cor.test(mean_alignment,cluster_abs_diff))


d_1_all %>%  lm(mean_alignment~cluster_min+cat_min+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary
d_1_all %>%  lm(mean_alignment~cluster_max+cat_min+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary
d_1_all %>%  lm(mean_alignment~cluster_abs_diff+cat_min+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary

```



### Figure of Exp1 alignment as a function of categoricality

```{r}
ggplot(d_1_all, aes(y=mean_alignment, x=cat_min, color=Condition, fill=Condition)) +
  geom_point(alpha=.25) +
  geom_smooth(method="lm", alpha=.25) +
  theme_bw() +
  ylab("Alignment") +
  xlab("Categoricality") +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  theme(text=element_text(size=20)) +
  theme(legend.position="top") +
	expand_limits(y=c(-.1,.7),x = c(-.1,1.05))+
  theme(panel.border = element_blank(), axis.line = element_line())

ggsave("plots/CEL_1_alignment_controlled_by_categoricality_scatter.pdf")
```


### Figure of alignment when controlling for categoricality

```{r, warning=FALSE, echo=TRUE,message = FALSE}
ggplot(d_1_all, aes(y=mean_alignment_adj, x=Condition, color=Condition, fill=Condition)) +
  geom_violin(alpha=.5) +
  geom_hline(data=means, aes(yintercept=Alignment, col=Condition), alpha=.5, size=1) +
  geom_boxplot(width=0.1, alpha=.5) +
  theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  ylab("Alignment after\ncontrolling for categoricality") +
  theme(text=element_text(size=20)) +
  theme(legend.position="top") +
  theme(panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())

ggsave("plots/CEL_1_alignment_controlled_by_categoricality_violin_mean.pdf")
```


# Study 2

```{r, warning=FALSE,message = FALSE}
indiv_df_2 <- read.csv(file="data/CEL_2_indiv_data.tsv", header=T, sep="\t") %>% 
	mutate(Condition = case_when(
		cond_numeric<0 ~ "Baseline",
		cond_numeric==0 ~ "No Labels",
		cond_numeric>0 ~ "With Labels"),
		exp="exp2")

pairwise_df_2 <- read.csv(file="data/CEL_2_pairwise_data.tsv", header=T, sep="\t")

```

## Effect of condition on categoricality measured as log(between/within)

Baseline is less categorical than no labels, but labels = no-labels

```{r, warning=FALSE,message = FALSE}
indiv_df_2 %>% group_by(Condition) %>% 
	summarize(Categoricality_mean = mean(log_cat_ratio),Categoricality_sd = sd(log_cat_ratio),n=n())

indiv_df_2 %>% lm(log_cat_ratio ~ relevel(as.factor(cond_numeric), ref='0'), data=.) %>% summary
indiv_df_2 %>% lm(log_cat_ratio ~ relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary

```
### Categoricality plot
```{r, warning=FALSE,message = FALSE, echo=TRUE}
means <- indiv_df_2 %>%
  group_by(Condition) %>%
  summarise(Categoricality = mean(log_cat_ratio))

ggplot(indiv_df_2, aes(y=log_cat_ratio, x=Condition, color=Condition, fill=Condition)) +
  geom_violin(alpha=.5) +
	scale_color_manual(values= colors) +
  scale_fill_manual(values= colors) +
  geom_hline(data=means, aes(yintercept=Categoricality, color=Condition), alpha=.5, size=1) +
  geom_boxplot(width=0.1, alpha=.5) +
  theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  ylab("Categoricality") +
  theme(text=element_text(size=20)) +
  theme(legend.position="blank") +
	coord_cartesian(ylim=c(-.05,3.3))+
  theme(panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())
  
ggsave("plots/CEL_2_categoricality_violin.pdf")

```


## Effect of condition on the number of clusters formed during free-sort

Number of clusters per condition

```{r}
indiv_df_2 %>%
  group_by(Condition) %>%
  summarise(Clusters = mean(n_clusters))

```



## Label participants produce a similar number of clusters on average to the other 2 conditions

Poisson model wins (shown by likelihood ratio test to be nearly identical to the negative binomial model)
```{r}
nb_counts <- indiv_df_2 %>% MASS::glm.nb(formula=n_clusters ~ relevel(as.factor(cond_numeric), ref='1'), data=.) 
poisson_counts <- indiv_df_2 %>% glm(formula=n_clusters ~ relevel(as.factor(cond_numeric), ref='1'), data=.,family=poisson)

pchisq(2 * (logLik(nb_counts) - logLik(poisson_counts)), df = 1, lower.tail = FALSE)
summary(poisson_counts)
```

Label people are significantly more likely to produce 2-cluster sorts

```{r, warning=FALSE,message = FALSE}
indiv_df_2 %>% group_by(Condition) %>% 
	summarize(two_cluster_sorts = mean(I(n_clusters==2)))

indiv_df_2 %>% glm(I(n_clusters==2) ~ relevel(as.factor(cond_numeric), ref='1'), data=.,family=binomial) %>% summary
```


### Plot Number of clusters

```{r, warning=FALSE,message = FALSE, echo=TRUE}

ggplot(indiv_df_2, aes(x=n_clusters, fill=Condition)) +
  geom_histogram(alpha=0.9,position="dodge", binwidth=0.5)+
  scale_x_continuous(breaks = seq(1, 10, 1))+
  scale_y_continuous(breaks = seq(0, 30, 5))+
  labs(caption = "", size=20) +  
  theme_minimal() +
  theme(panel.grid.major = element_blank()) +
  theme(panel.grid.minor = element_blank()) +
  geom_hline(yintercept = c(0,5,10,15,20,25), alpha = 0.15) +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  ylab("Frequency") + 
  xlab("Number of clusters used") +
	coord_cartesian(ylim=c(0,30),xlim=c(2,9))+
  theme(axis.text.x = element_text(size=13),
       axis.title.y = element_text(size=15),
       axis.title.x = element_text(size=15))+
  theme(legend.position = c(.4, .7))

ggsave("plots/CEL_2_n_clusters_histogram.pdf")
```

## Effect of condition on alignment (aggregated by participant)

Alignment significantly higher in with labels, compared with no labels and baseline

```{r, warning=FALSE,message = FALSE}

pairwise_df_2 <- pairwise_df_2 %>% 
	mutate(cat_min = pmin(cat_diff_log_ratio_a, cat_diff_log_ratio_b),
				 cluster_min = pmin(pp_a_n_clusters, pp_b_n_clusters),
				 cluster_max = pmax(pp_a_n_clusters, pp_b_n_clusters),
				 cluster_abs_diff = abs(pp_a_n_clusters-pp_b_n_clusters)
				 )


d_2a <- pairwise_df_2 %>%
  group_by(cond_numeric,Condition,participant_a) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>%
  rename(participant = participant_a)
d_2b <- pairwise_df_2 %>%
  group_by(cond_numeric,Condition,participant_b) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>%
  rename(participant = participant_b)
d_2_all <- rbind(d_2a,d_2b) %>%
  group_by(cond_numeric,Condition,participant) %>%
  summarize_if(is.numeric,mean,na.rm=TRUE) %>% 
	rename(mean_alignment = z_transformed_rank_r)

#residualize categoricality from alignment for later analysis
d_2_all$mean_alignment_adj <- resid(lm(mean_alignment ~ cat_min, data=d_2_all))
d_2_all$exp <- "exp2"

```

## Alignment analyses
```{r}
means <- d_2_all %>%
  group_by(Condition) %>%
  summarise(Alignment = mean(mean_alignment),Alignment_sd=sd(mean_alignment))

means
lm(formula=mean_alignment ~ relevel(as.factor(cond_numeric), ref='1'), data=d_2_all) %>% summary
lm(formula=mean_alignment ~ relevel(as.factor(cond_numeric), ref='0'), data=d_2_all) %>% summary

```


### Alignment plot

```{r, warning=FALSE,message = FALSE, echo=TRUE}

ggplot(d_2_all, aes(y=mean_alignment, x=Condition, color=Condition, fill=Condition)) +
  geom_violin(alpha=.5) +
  geom_hline(data=means, aes(yintercept=Alignment, col=Condition), alpha=.5, size=1) +
  geom_boxplot(width=0.1, alpha=.5) +
  theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  ylab("Alignment") +
  theme(text=element_text(size=20)) +
  theme(legend.position="blank") +
	coord_cartesian(ylim=c(-.05,.7))+
  theme(panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())
  
ggsave("plots/CEL_2_alignment_violin.pdf")
```


## Effect of condition on alignment controlling for minimum categoricality by pair

After controlling for minimum categoricality (by pair), we still see (weakened) effects of condition on alignment: participants in the with labels condition have higher alignment of sorts than participants in the no labels and baseline conditions.

```{r, warning=FALSE,message = FALSE}
d_2_all %>% lm(formula=mean_alignment ~ cat_min+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary
d_2_all %>% lm(formula=mean_alignment ~ cat_min+relevel(as.factor(cond_numeric), ref='0'), data=.) %>% summary
```


### Plot Exp2 alignment as a function of categoricality

```{r}
ggplot(d_2_all, aes(y=mean_alignment, x=cat_min, color=Condition, fill=Condition)) +
  geom_point(alpha=.25) +
  geom_smooth(method="lm", alpha=.25) +
  theme_bw() +
  ylab("Alignment") +
  xlab("Categoricality") +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  theme(text=element_text(size=20)) +
  theme(legend.position="top") +
	expand_limits(y=c(-.1,.7),x = c(-.1,1.05))+
  theme(panel.border = element_blank(), axis.line = element_line())

ggsave("plots/CEL_2_alignment_controlled_by_categoricality_scatter.pdf")
```
### Plot of residualized alignment

```{r, warning=FALSE, echo=TRUE,message = FALSE}

means <- d_2_all %>% group_by(Condition) %>% summarize(Alignment=mean(mean_alignment_adj))

ggplot(d_2_all, aes(y=mean_alignment_adj, x=Condition, color=Condition, fill=Condition)) +
  geom_violin(alpha=.5) +
  geom_hline(data=means, aes(yintercept=Alignment, col=Condition), alpha=.5, size=1) +
  geom_boxplot(width=0.1, alpha=.5) +
  theme_bw() +
  scale_fill_manual(values=colors) +
  scale_color_manual(values=colors) +
  ylab("Alignment after\ncontrolling for categoricality") +
  theme(text=element_text(size=20)) +
  theme(legend.position="top") +
  theme(panel.grid.major.x = element_blank(), panel.grid.minor.x = element_blank()) +
  theme(panel.border = element_blank(), axis.line = element_line())

ggsave("plots/CEL_2_alignment_controlled_by_categoricality_violin.pdf")
```



## Effect of condition on alignment controlling for minimum categoricality by pair

After controlling for minimum categoricality by pair, no differences in alignment across conditions
```{r, warning=FALSE,message = FALSE}

d_2_all %>%  lm(mean_alignment~cat_min, data=.) %>% summary
d_2_all %>%  with(cor(mean_alignment,cat_min))

d_2_all %>%  lm(mean_alignment~cat_min+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary
```


## Effect of condition on alignment controlling for cluster nums

After controlling for minimum categoricality by pair, no differences in alignment across conditions
```{r, warning=FALSE,message = FALSE}

d_2_all %>%  with(cor.test(mean_alignment,cluster_min))
d_2_all %>%  with(cor.test(mean_alignment,cluster_max))
d_2_all %>%  with(cor.test(mean_alignment,cluster_abs_diff))


d_2_all %>%  lm(mean_alignment~cat_min+cluster_min+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary
d_2_all %>%  lm(mean_alignment~cat_min+cluster_max+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary
d_2_all %>%  lm(mean_alignment~cat_min+cluster_abs_diff+relevel(as.factor(cond_numeric), ref='1'), data=.) %>% summary

```


# Comparisons of Exps 1 and 2

## Comparison of categoricality between exps 1 and 2

```{r}
bind_rows(indiv_df_1,indiv_df_2) %>% lm(log_cat_ratio~exp,data=.) %>% summary
bind_rows(indiv_df_1,indiv_df_2) %>% filter(Condition=="No Labels") %>% lm(log_cat_ratio~exp,data=.) %>% summary

```

## Comparison of likelihood of binary sorts 

```{r}
bind_rows(indiv_df_1,indiv_df_2) %>% glm(I(n_clusters==2)~exp,data=.,family=binomial) %>% summary
```

## Comparison of alignment between exps 1 and 2

```{r}
bind_rows(d_1_all,d_2_all) %>% lm(mean_alignment~exp,data=.) %>% summary
bind_rows(d_1_all,d_2_all) %>% group_by(Condition,exp) %>% 
	summarize(mean_alignment=mean(mean_alignment)) %>%
	pivot_wider(names_from=exp,values_from = mean_alignment) %>% 
	mutate(exp2_alignment_advantage = exp2-exp1)
```

