---
title: "Pre-exposure (Match-to-sample)"
date: "6/13/2023"
output: 
  html_document:
    number_sections: false
    theme: cerulean
    toc_float: true
    toc: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Load libraries

```{r, include=FALSE}
library(dplyr)
library(lme4)
library(lmerTest)
```

## Load in data from in-lab and online studies

Remember that the in-lab match to sample was about 3x as long as online version, hence more observations

```{r, include=FALSE}
match_to_sample_exp1 <- read.csv(file="s1_match_to_sample.csv",header=T, sep=",")
match_to_sample_exp2 <- read.csv(file="s2_match_to_sample.csv", header=T, sep=",")

exp2_successful_sorters <- read.csv(file="../2_sort_task/data/CEL_2_indiv_data.tsv", header=T, sep="\t") %>% select(participant)

```

# Study 1

## Acurracy

No significant differences by labeling condition

```{r, warning=FALSE, echo=FALSE}
match_to_sample_exp1 %>%
  group_by(subjCode,label_cond) %>%
  summarize(isRight = mean(isRight)) %>% 
	group_by(label_cond) %>%
  summarize(isRight_mean = mean(isRight),
            isRight_sd = sd(isRight),n=n())



m1_accu <- glmer(isRight~label_cond + (1|subjCode),
                data=match_to_sample_exp1,control = glmerControl(optCtrl=list(maxfun=6e4)),
                family=binomial(link="logit"))
summary(m1_accu)
```

## RTs

Trimmed to exclude <150 ms or 2SDs above the mean

```{r, echo=FALSE}
#include only correct trials
match_to_sample_exp1 <- match_to_sample_exp1 %>% filter(isRight==1) %>%
	group_by(label_cond) %>% mutate(subj_mean_RT=mean(RT,na.rm=TRUE),subj_sd_RT = sd(RT)) %>% 
	mutate(exclude_outlier_RT = RT > subj_sd_RT*2 | RT<150) %>% 
	mutate(exp="exp1")


match_to_sample_exp1 %>% 	filter(exclude_outlier_RT==FALSE) %>% 
	group_by(subjCode,label_cond) %>% summarize(subj_mean_RT=mean(RT,na.rm=TRUE)) %>%  
	group_by(label_cond) %>% summarize(cond_RT_mean=mean(subj_mean_RT),cond_RT_SD = sd(subj_mean_RT),n=n())


match_to_sample_exp1 %>% 	filter(exclude_outlier_RT==FALSE) %>% 
	lmer(RT~label_cond+(1|subjCode),data=.) %>% summary



```

# Study 2

## Remove participants who sorted improperly

Those participants were excluded based on faulty sorts, but still included in these data, so let's exclude them.

```{r}

match_to_sample_exp2 <- match_to_sample_exp2 %>% filter(subjCode %in% exp2_successful_sorters$participant)
```


## Acurracy

No significant differences by labelling condition

```{r, warning=FALSE, echo=FALSE}
match_to_sample_exp2 %>% 
  group_by(subjCode,label_cond) %>%
  summarize(isRight = mean(isRight)) %>% 
	group_by(label_cond) %>%
  summarize(isRight_mean = mean(isRight),
            isRight_sd = sd(isRight),n=n())


match_to_sample_exp2 %>%
	glmer(isRight~1+label_cond + (1|subjCode),
                data=.,control = glmerControl(optCtrl=list(maxfun=6e4)),
                family=binomial) %>% summary
```

## RTs

```{r, echo=FALSE}

#include only correct trials
match_to_sample_exp2 <- match_to_sample_exp2 %>% filter(isRight==1) %>%
	group_by(label_cond) %>% mutate(subj_mean_RT=mean(RT,na.rm=TRUE),subj_sd_RT = sd(RT)) %>% 
	mutate(exclude_outlier_RT = RT > subj_sd_RT*2 | RT<150) %>% 
	mutate(exp="exp2")

match_to_sample_exp2 %>% 	filter(exclude_outlier_RT==FALSE) %>% 
	group_by(subjCode,label_cond) %>% summarize(subj_mean_RT=mean(RT,na.rm=TRUE)) %>%  
	group_by(label_cond) %>% summarize(cond_RT_mean=mean(subj_mean_RT),cond_RT_SD = sd(subj_mean_RT),n=n())

match_to_sample_exp2 %>% 	filter(exclude_outlier_RT==FALSE) %>% 
	lmer(RT~label_cond+(1|subjCode),data=.) %>% summary

```

# Compare RTs of exp 1 vs exp 2 
```{r}
rbind(match_to_sample_exp1,match_to_sample_exp2) %>% 
	filter(exclude_outlier_RT==FALSE) %>% 
	lmer(RT~exp+(1|subjCode),data=.) %>% summary
```

